NumPy---Array Programming in Python

### 2020-01-26 body.tex
Fix typo

For example, the \code{eht-imaging} library developed by the Event Horizon Telescope 
collaboration relies on many components of the scientific Python ecosystem.
NumPy arrays are used to store and manipulate numerical data at every step
in the processing chain: from raw data through calibration and image 
reconstruction.
Scipy is used to provide tools used in general image processing such as 
filtering and image alignment, while scikit-image provided higher-level
functionality such as edge filters and Hough transforms.
SciPy provides fundamental algorithms for scientific computing on arrays
including many mathematical, scientific, and engineering routines.
SciPy and NumPy are closely related and were developed together often
by the same people.
scikit-image is a popular technique-specific library,
which vastly extends the basic image processing tools provided by SciPy.
Other components of Scipy are used throughout the library, such as the
\code{scipy.optimize} package for handling general optimization tasks.
NetworkX \cite{SciPyProceedings_11} (the standard package for complex
network analysis) is used for image comparisons.
Astropy \cite{astropy:2013, astropy:2018} (a community-developed astronomy
libarary) is used in quite a few places,
primarily for I/O and time/coordinate transformations.
Matplotlib (the core library for generating publication-ready figures
and visualizations) is used for visualizing data throughout the analysis pipeline,
including the generation of the final image of the black hole.
% N.B. - most of this comes from introspecting the Image class defined in
% ehtim/image.py.

>>>>

For example, the \code{eht-imaging} library developed by the Event Horizon Telescope 
collaboration relies on many components of the scientific Python ecosystem.
NumPy arrays are used to store and manipulate numerical data at every step
in the processing chain: from raw data through calibration and image 
reconstruction.
Scipy is used to provide tools used in general image processing such as 
filtering and image alignment, while scikit-image provides higher-level
functionality such as edge filters and Hough transforms.
SciPy provides fundamental algorithms for scientific computing on arrays
including many mathematical, scientific, and engineering routines.
SciPy and NumPy are closely related and were developed together often
by the same people.
scikit-image is a popular technique-specific library,
which vastly extends the basic image processing tools provided by SciPy.
Other components of Scipy are used throughout the library, such as the
\code{scipy.optimize} package for handling general optimization tasks.
NetworkX \cite{SciPyProceedings_11} (the standard package for complex
network analysis) is used for image comparisons.
Astropy \cite{astropy:2013, astropy:2018} (a community-developed astronomy
libarary) is used in quite a few places,
primarily for I/O and time/coordinate transformations.
Matplotlib (the core library for generating publication-ready figures
and visualizations) is used for visualizing data throughout the analysis pipeline,
including the generation of the final image of the black hole.
% N.B. - most of this comes from introspecting the Image class defined in
% ehtim/image.py.
